\Title

### 2021-05-14 latex/paper/main.tex
Made the draft a one column, double spaced format for Manfredi.

\documentclass[journal,twoside,web]{ieeecolor}

@@

In this article we redeveloped the framework of virtual nonholonomic
constraints for underactuated mechanical systems.
We applied this framework towards the acrobot, and designed a constraint which
emulates giant motion from gymnastics.
We proved this constraint will inject energy into the simplified acrobot whose
limbs are massless rods of equal length, with equal masses at the tips.
We then performed simulations and physical experiments of this VNHC.
These demonstrated that virtual nonholonomic constraints are capable of
injecting and dissipating energy in a robust manner, all while producing
realistic biological motion.

>>>>

% TODO: remove onecolumn and draftcls formatting
\documentclass[journal,twoside,onecolumn,draftclsnofoot,web]{ieeecolor}

@@

In this article we redeveloped the framework of virtual nonholonomic
constraints for underactuated mechanical systems with arbitrary degree of
underactuation.
We applied this framework towards the acrobot, and designed a constraint which
emulates giant motion from gymnastics.
We proved this constraint will inject energy into the simplified acrobot whose
limbs are massless rods of equal length, with equal masses at the tips.
We then performed simulations and physical experiments of this VNHC.
These demonstrated that virtual nonholonomic constraints are capable of
injecting and dissipating energy in a robust manner, all while producing
realistic biological motion.
